\documentclass[margin]{res}

% Default font is the helvetica postscript font
\usepackage{helvet}

\usepackage[pdftex,
            pdfauthor={Kenneth Berland},
            pdftitle={Kenneth Berland Resume},
            pdfkeywords={kenneth berland some easter eggs for pdfinfo people},
            pdfproducer={Latex},
            pdfcreator={pdflatex}]{hyperref}

% Increase text height
\textheight=700pt

\begin{document}

%-------------------------------------------------------------------------------
%	NAME AND ADDRESS SECTION
%-------------------------------------------------------------------------------
%--------------------TITLE-------------
\name{\huge Kenneth Berland}
\bigskip

\address{2528 Chilton Way\\ken@hero.net}
\address{Berkeley, CA 94704\\(310) 383-7981}

\begin{resume}

%-------------------------------------------------------------------------------
% Modify the format of each position
\begin{format}
\title{l}\employer{r}\\
\dates{l}\location{r}\\
\body\\
\end{format}
%-------------------------------------------------------------------------------

\section{EXPERIENCE}

\employer{Modelcode.ai}
\location{San Francisco, CA}
\dates{December 2023\textendash December 2024}
\title{\textbf{VP of Infrastructure}}
\begin{position}
\hspace*{.5cm}Lead innovation and infrastructure engineering for model-based modernization of legacy codebases. As the first production software engineer, I've built our framework for LLM and workflow automation, application infrastructure, deployment, scaling, and monitoring.
\end{position}

\employer{Amazon Music}
\location{San Francisco, CA}
\dates{February 2017\textendash November 2023}
\title{\textbf{Sr. Manager, Software Dev. (L7)}}
\begin{position}
\hspace*{.25cm}Leader of the Playback team at Amazon Music. Flawless music and podcast playback for 60 million customers. Negotiated technical aspects of major-label contracts (Sony, UMG, and Warner) to match security, technical specs, and capabilities. Developed, launched, and maintained Dolby Atmos and Sony spatial playback. Directed streaming security including encryption, cryptography choices, and authentication. Owned all music licensing and delivery services across phones, tablets, desktops, FireTV, set-top boxes, and 100 million Echo devices. 
\end{position}

\employer{Grand Rounds, Inc.}
\location{San Francisco, CA}
\dates{2013\textendash November 2016}
\title{\textbf{Vice President of Engineering}}
\begin{position}
\hspace*{.5cm}Founding member and Head of Engineering. Built and led Engineering while simultaneously developing and delivering the Company's products. Directed HIPAA, SOC-2, and NIST compliance. Chaired the Information Security Committee.
\end{position}


\employer{United States Court of Appeals for the Sixth Circuit}
\location{Louisville, KY}
\dates{2005\textendash2006}
\title{\textbf{Clerk to Danny J. Boggs, Chief Judge}}
\begin{position}
\hspace*{.5cm}Researched and analyzed federal and state law issues requiring decision by the court including: patent, copyright and trademark; labor and employment; contracts; sovereign immunity and state’s rights; immigration; and death penalty and criminal law. Drafted opinions and orders consistent with the Court’s rulings.
\end{position}

\employer{Hero Consulting}
\location{Los Angeles, CA}
\dates{1998\textendash2003}
\title{\textbf{Partner}}
\begin{position}
\hspace*{.5cm}Consultant for digital feature film and television commercial production. Designed and implemented custom rendering solutions in C. Film projects included \textit{The Core, Pearl Harbor and Driven}. Television commercial projects included Energizer \textit{Titanium} and AT\&T \textit{Ants}.
\end{position}

\employer{Twentieth Century Fox}
\location{Los Angeles, CA}
\dates{1996\textendash1998}
\title{\textbf{Technical Director}}
\begin{position}
\hspace*{.5cm}Created digital effects for feature films including \textit{Volcano, Jingle all the Way, and Face/Off}. Supervised teams in creating systems for the visualization of special effects. Provided in-house consulting for complex aspects of digital film-making.
\end{position}

\employer{Rutt Video}
\location{New York, NY}
\dates{1993\textendash1995}
\title{\textbf{Technical Director}}
\begin{position}
\hspace*{.5cm}Created digital effects using Silicon Graphics (SGI) hardware under the mentorship of Steve Rutt.
\end{position}

\employer{Michael Lavine Photography}
\location{New York, NY}
\dates{1991\textendash1993}
\title{\textbf{First Assistant}}
\begin{position}
\hspace*{.5cm}On-camera first assistant to world-renown rock photographer. Sessions with Nirvana, Pearl Jam, the Ramones, Sonic Youth, Iggy Pop, Smashing Pumpkins, and more.
\end{position}


\section{EDUCATION}

\textbf{University of Southern California}, Los Angeles, CA\\
{\sl Juris Doctor}\hfill Order of the Coif
(top 10\%)
\\
  Proposed a \href{https://hero.net/public/Triple_Play.pdf}{regulatory framework for broadband}.

\textbf{University of Wisconsin, Madison}, Madison, WI\\
{\sl Bachelor of Science}

\end{resume}
\end{document}
