\documentclass[margin]{res}

% Default font is the helvetica postscript font
\usepackage{helvet}

\usepackage[pdftex,
            pdfauthor={Kenneth Berland},
            pdftitle={Kenneth Berland Resume},
            pdfkeywords={kenneth berland some easter eggs for pdfinfo people},
            pdfproducer={Latex},
            pdfcreator={pdflatex}]{hyperref}

% Increase text height
\textheight=700pt

\begin{document}

%-------------------------------------------------------------------------------
%	NAME AND ADDRESS SECTION
%-------------------------------------------------------------------------------
%--------------------TITLE-------------
\name{\huge Kenneth Berland}
\bigskip

\address{2528 Chilton Way\\ken@hero.net}
\address{Berkeley, CA 94704\\(310) 383-7981}

\begin{resume}

%-------------------------------------------------------------------------------
% Modify the format of each position
\begin{format}
\title{l}\employer{r}\\
\dates{l}\location{r}\\
\body\\
\end{format}
%-------------------------------------------------------------------------------

\section{EXPERIENCE}

\employer{Modelcode.ai}
\location{San Francisco, CA}
\dates{December 2023\textendash current}
\title{\textbf{VP of Infrastructure}}
\begin{position}
\hspace*{.5cm}Lead innovation and infrastructure engineering for model-based modernization of legacy codebases. As the first production software engineer, I've built our framework for LLM and workflow automation, application infrastructure, deployment, scaling, and monitoring.
\end{position}
\employer{Amazon Music}
\location{San Francisco, CA}
\dates{February 2017\textendash November 2023}
\title{\textbf{Sr. Manager, Software Dev. (L7)}}
\begin{position}
\hspace*{.25cm}Leader of the Playback team at Amazon Music. Flawless music and podcast playback for 60 million customers. Hands-on management of complex C++, Java, and Python products. Develop engineering leaders within my 35-person org. Developed, launched, and maintained Dolby Atmos and Sony spatial playback. Directed streaming security including encryption, cryptography choices, and authentication. Owned all music licensing and delivery services across phones, tablets, desktops, FireTV, set-top boxes, and 100 million Echo devices. 
\end{position}

\employer{Grand Rounds, Inc.}
\location{San Francisco, CA}
\dates{2013\textendash November 2016}
\title{\textbf{Vice President of Engineering}}
\begin{position}
\hspace*{.5cm}Founding member and Head of Engineering. Built and led Engineering while simultaneously developing and delivering the Company's products. Directed HIPAA, SOC-2, and NIST compliance. Chaired the Information Security Committee. Sourced and hired 39 engineers, including Architect, Directors, and individual contributors. Implemented a Lean system to deliver new products and features. Managed several teams and eliminated cross-team dependencies.
\end{position}

\employer{Servio, Inc.}
\location{San Francisco, CA}
\dates{2012\textendash2013}
\title{\textbf{Vice President of Engineering}}
\begin{position}
\hspace*{.5cm}Led Engineering team. Identified and led execution of a technical roadmap that extracted and surfaced costs from a complex crowd-souring system.
\end{position}

\employer{Reputation.com}
\location{Redwood City, CA}
\dates{2011\textendash2012}
\title{\textbf{Vice President of Engineering}}
\begin{position}
\hspace*{.5cm}Led the company's 34-person Engineering team. Managed, streamlined, and improved software development and operations across all of the company's core technologies.
\end{position}

\employer{Hero.com}
\location{San Francisco, CA}
\dates{2008\textendash2011}
\title{\textbf{Lead Engineer and Product Manager}}
\begin{position}
\hspace*{.5cm}Designed a cloud-based content management and content review web application for attorneys and forensic accountants.  Managed teams of remote engineers. Quadrupled annual gross revenue in one year. Early AWS adopter\textemdash horizontally scaled document processing over 100's of EC2 workers.
\end{position}


\section{EDUCATION}

\textbf{University of Southern California}, Los Angeles, CA\\
{\sl Juris Doctor}\hfill Order of the Coif
(top 10\%)
\\
{\sl Southern California Law Review, Articles Editor. Licensed to practice law in California}

\textbf{University of Wisconsin, Madison}, Madison, WI\\
{\sl Bachelor of Science}

\end{resume}
\end{document}
