\documentclass[margin]{res}

% Default font is the helvetica postscript font
\usepackage{helvet}

\usepackage[pdftex,
            pdfauthor={Kenneth Berland},
            pdftitle={Resume},
            pdfkeywords={kenneth berland some easter eggs for pdfinfo people},
            pdfproducer={Latex},
            pdfcreator={pdflatex}]{hyperref}

% Increase text height
\textheight=700pt

\begin{document}

%-------------------------------------------------------------------------------
%	NAME AND ADDRESS SECTION
%-------------------------------------------------------------------------------
%--------------------TITLE-------------
\name{\huge Kenneth Berland}
\bigskip

\address{2528 Chilton Way\\ken@hero.net}
\address{Berkeley, CA 94704\\(310) 383-7981}

\begin{resume}

%-------------------------------------------------------------------------------
% Modify the format of each position
\begin{format}
\title{l}\employer{r}\\
\dates{l}\location{r}\\
\body\\
\end{format}
%-------------------------------------------------------------------------------

\section{EXPERIENCE}

\employer{Amazon Music}
\location{San Francisco, CA}
\dates{February 2019\textendash current}
\title{\textbf{Sr. Manager, Software Dev.}}
\begin{position}
\hspace*{.5cm}Single-threaded leader of the 27-person Playback Experience team at Amazon Music. Developing and maintaining Music's Tier-1 location, delivery, and licensing, services, native music players for iOS, Android, FireTV, Web, Mac, and Windows desktops, and web-based clients. Music delivery service for over 100MM Echo devices. Developed, launched, and maintaining Dolby Atmos and Sony spatial playback. Negotiating major-label contracts to match technical specifications and capabilities.
\end{position}

\employer{Amazon.com}
\location{San Francisco, CA}
\dates{February 2017\textendash February 2019}
\title{\textbf{Sr. Manager, Software Dev.}}
\begin{position}
\hspace*{.5cm}Single-threaded leader of the 26-member AUI team and and 10-member AUIQA teams. Manager of managers in SFO, SEA, and BLR. Simultaneously supporting over 800 teams that rely upon AUI to deliver a consistent experience for Amazon shoppers and developing the next generation of rendering libraries to support the growth of the retail website. Realized \$507MM annualized OPS through roadmap efforts in Q1 and Q2 of 2018 through site-wide UX changes.
\end{position}

\employer{Grand Rounds, Inc.}
\location{San Francisco, CA}
\dates{2013\textendash November 2016}
\title{\textbf{Vice President of Engineering}}
\begin{position}
\hspace*{.5cm}Founding member and Head of Engineering team.  Built and led Engineering while simultaneously developing and delivering the Company's products. Sourced and hired 39 engineers, including Architect, Directors, and individual contributors.  Implemented a Lean system to deliver new products and features. Managed several teams and eliminated cross-team dependencies.  Ensured HIPAA compliance and chaired the Information Security Committee.  
\end{position}

\employer{Servio, Inc.}
\location{San Francisco, CA}
\dates{2012\textendash2013}
\title{\textbf{Vice President of Engineering}}
\begin{position}
\hspace*{.5cm}Led Engineering team. Identified and led execution of a technical road-map that extracted and surfaced costs from a complex crowd-souring system.
\end{position}

\employer{Reputation.com}
\location{Redwood City, CA}
\dates{2011\textendash2012}
\title{\textbf{Vice President of Engineering}}
\begin{position}
\hspace*{.5cm}Led the Company's 34-person Engineering team. Managed, streamlined, and improved software development and operations across all of the Company's core technologies.
\end{position}

\employer{Hero.com}
\location{San Francisco, CA}
\dates{2008\textendash2011}
\title{\textbf{Lead Engineer and Product Manager}}
\begin{position}
\hspace*{.5cm}Designed a cloud-based content management and content review web application for attorneys and forensic accountants.  Managed teams of remote engineers. Grew product to \$200,000 in annual gross revenue. Early AWS adopter\textemdash horizontally scaled document processing over 100's of EC2 workers.
\end{position}


\section{EDUCATION}

\textbf{University of Southern California}, Los Angeles, CA\\
{\sl Juris Doctor}\hfill Order of the Coif
(top 10\%)
\\
{\sl Southern California Law Review, Articles Editor. Licensed to practice law in California}

\textbf{University of Wisconsin, Madison}, Madison, WI\\
{\sl Bachelor of Science}

\end{resume}
\end{document}
