\documentclass[margin]{res}

% Default font is the helvetica postscript font
\usepackage{helvet}

\usepackage[pdftex,
            pdfauthor={Kenneth Berland},
            pdftitle={Kenneth Berland Resume},
            pdfkeywords={kenneth berland some easter eggs for pdfinfo people},
            pdfproducer={Latex},
            pdfcreator={pdflatex}]{hyperref}
\usepackage{hyperref}

% Increase text height
\textheight=700pt

\begin{document}

%-------------------------------------------------------------------------------
%	NAME AND ADDRESS SECTION
%-------------------------------------------------------------------------------
%--------------------TITLE-------------
\name{\huge Kenneth Berland}
\address{2528 Chilton Way\\ken@hero.net}
\address{Berkeley, CA 94704\\(310) 383-7981}

\begin{resume}

%-------------------------------------------------------------------------------
% Modify the format of each position
\begin{format}
\title{l}\employer{r}\\
\dates{l}\location{r}\\
\body\\
\end{format}
%-------------------------------------------------------------------------------

\section{EXPERIENCE}

\employer{Modelcode.ai}
\location{San Francisco, CA}
\dates{December 2023\textendash current}
\title{\textbf{VP of Infrastructure}}
\begin{position}
\hspace*{.25cm}Lead infrastructure engineering for model-based modernization of legacy codebases. As the first production engineer, I've built our frameworks for LLM and workflow automation, application infrastructure, deployment, scaling, and monitoring.
\end{position}

\employer{Amazon Music}
\location{San Francisco, CA}
\dates{February 2017\textendash November 2023}
\title{\textbf{Sr. Manager, Software Dev.}}
\begin{position}
\hspace*{.25cm}Leader of the Playback team at Amazon Music. Flawless music and podcast playback for 60 million customers. Negotiated technical aspects of major-label contracts (Sony, UMG, and Warner) to match security, technical specs, and capabilities. Developed, launched, and maintained Dolby Atmos and Sony spatial playback. Directed streaming security including encryption, cryptography choices, and authentication. Owned all music licensing and delivery services across phones, tablets, deskstops, FireTV, set-top boxes, and 100 million Echo devices. 
\end{position}

\employer{Grand Rounds, Inc.}
\location{San Francisco, CA}
\dates{2013\textendash November 2016}
\title{\textbf{Vice President of Engineering}}
\begin{position}
\hspace*{.25cm}Founding member and Head of Engineering team. Built and led Engineering while simultaneously developing and delivering the Company's products. Directed HIPAA, SOC-2, and NIST compliance. Chaired the Information Security Committee. Sourced and hired 39 engineers, including Architect, Directors, and individual contributors. Implemented a Lean system to deliver new products and features. Managed several teams and eliminated cross-team dependencies.
\end{position}

\employer{Hero—Legal eDiscovery \& Transactions}
\location{San Francisco, CA}
\dates{2008\textendash2011}
\title{\textbf{Founder and CTO}}
\begin{position}
\hspace*{.25cm}Led engineering, designed, built, and deployed 1) a cloud-based content management and content review web application for attorneys and forensic accountants.\href{https://hero.net/public/demo.html}{Demo}; and 2) a social workspace for attorneys to speed transactions. \href{https://hero.net/public/tour.html}{Demo}. Grew both products to over \$200,000 ARR each.
\end{position}

\employer{Howard Rice}
\location{San Francisco, CA}
\dates{2007\textendash2008}
\title{\textbf{Business Associate}}
\begin{position}
\hspace*{.25cm}Structured and drafted venture capital financing transactions. Wrote, reviewed, and negotiated documents for business transactions. Extensive work negotiating software and digital content licensing for both licensors and licensees. Negotiated legal terms for services agreements and strategic business alliances.
\end{position}

\employer{Twentieth Century Fox/VIFX}
\location{Los Angeles, CA}
\dates{1998\textendash2003}
\title{\textbf{Technical Director}}
\begin{position}
\hspace*{.25cm}Created digital effects for feature films (including {\it{Face/Off}}, {\it{Jingle all the Way}}, {\it{Pearl Harbor}}, and {\it{Volcano}}) and television commericals invcluding the \href{https://vimeo.com/6690467}{Energizer Bunny}, \href{https://vimeo.com/16943264}{Jeep}, and AT\&T. Supervised teams in creating systems for the visualization of special effects. Provided in-house consulting for complex aspects of digital film-making. Designed and implemented custom rendering solutions in C.
\end{position}


\section{EDUCATION}

\textbf{University of Southern California}, Los Angeles, CA\\
{\sl Juris Doctor}\hfill Order of the Coif
(top 10\%)
\\
{\sl Southern California Law Review, Articles Editor. Licensed to practice law in California}

\textbf{University of Wisconsin, Madison}, Madison, WI\\
{\sl Bachelor of Science}

\end{resume}
\end{document}
